What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
more

\begin{document}

\title{What we {\sf eval} in the shadows}
\subtitle{A large-scale study of {\sf eval} usage in R programs}

%% Aviral Goel
%% Pierre Donat-Bouillud
%% Filip Krikava
%% Jan Vitek

%% What is the right order?

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}
\orcid{}
\author{Author}
\authornotemark[1]
\email{r@s.com}
\affiliation{%
	\institution{Institute for Clarity in Documentation}
	\streetaddress{P.O. Box 1212}
	\city{Dublin}
	\state{Ohio}
	\country{USA}
	\postcode{43017-6221}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

@@

Our corpus is assembled from three sources. Firstly, we start with the
\emph{Base} libraries that are bundled with the language implementation.
Secondly, we acquire packages hosted on \emph{CRAN}. Thirdly, we downloaded
scripts from \emph{Kaggle}.

\mypara{Base.} The base dataset contains 13 libraries performing basic
arithmetics, statistics, and operating system related functionalities.

\mypara{CRAN.} The Comprehensive R Archive
Network,\footnote{\url{cran.r-project.org}} or CRAN, is the largest curated
repository of R packages. It hosts \CranAvailablePackagesRnd packages with 6 new
packages submitted each day~\cite{Ligges2017}. Packages that are accepted to
CRAN are authored by experienced developers and they must abide to a number of
well-formedness rules automatically checked on each commit. Furthermore, each
package comes with sample data and tests. There are three sources of runnable
code for each package: \emph{tests, examples} and \emph{vignettes} --
respectively, unit tests, executable code snippets from the documentation, and
long-form executable use-cases written in Markdown. Examples and vignettes can
be turned into scripts by extracting the relevant code. We obtained
\CranPackages that call \eval. These packages represent \CranPackagesRatio of
all packages or \CranCodeRatio of the entire code size of CRAN. From these we
extracted \CranRunnableScripts scripts that contain \CranRunnableCode lines of
code (\CranRunnableCodeExamplesRnd in examples, \CranRunnableCodeVignettesRnd in
vignettes and \CranRunnableCodeTestsRnd in tests).

@@

The analysis presented in this has been automated by a pipeline that acquires
packages, extract scripts, executes them, traces their behavior and summarizes
observations. Figure~\ref{fig:pipeline} shows the main steps along with their
running time, data size, and number of elements manipulated. Timings are from a
cluster of three 2.3GHz Intel Xeon 6140 servers, with 72 cores and 256GB of RAM,
and shared OCFS network storage.

@@

\noindent The pipeline steps are:
\medskip
\begin{compactenum}
\item \emph{Download.} Packages are downloaded automatically from CRAN. For
  scripts, a web crawler retrieves code and the Kaggle command line tool
  downloads data. Installation is complicated by native dependencies which
  are not properly documented and thus hard to automatically resolve.
\item \emph{Extract.} Given installed packages and scripts, the next step is to
  create runnable programs. The \genthat tool helpfully extracts all runnable
  code snippets from a package and turns each of these into a self-standing
  program~\cite{issta18}. Some Kaggle kernels are already scripts, for those
  nothing more needs be done. Others kernels are packages as notebooks, either
  as Rmarkdown or Jupyter, for those we use \c{knitr} to extract runnable code.
  The body of each extracted program is instrumented with calls our dynamic
  analyzer to ensure that we only record calls to \eval from the code of
  interest and not from bootstrapping or execution harness operations.
\item \emph{Trace.} Each program is executed using our dynamic analysis tool
  which is heavily instrumented interpreter that captures calls to \eval and
  many other fine-grained runtime events. Packages are run twice, once to
  capture \eval calls originating from package code, and a second time to
  capture calls coming from the base libraries. To avoid any interference, each
  program is run in its own process.
\item \emph{Analyze.} Finally, analysis output is merged, cleaned and summarized
  in a post-processing phase driven by series of R scripts. The summarized data
  is then analyzed in RMarkdown notebooks to gather insights. All figures and
  numbers appearing in the paper are generated automatically. Figures are
  produced in PDF by \c{ggplot2}, numbers are exported as \LaTeX macros.
\end{compactenum}

@@

@@

\begin{figure}[h!]
 \includegraphics[width=0.5\textwidth, trim=4.8cm 0 6cm 0, clip]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{figure}

>>>>

\begin{document}
\title{What we {\sf eval} in the shadows}
\subtitle{A large-scale study of {\sf eval} usage in R programs}

%% Aviral Goel
%% Pierre Donat-Bouillud
%% Filip Krikava
%% Jan Vitek
%% What is the right order?

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}
\orcid{}
\author{Author}
\authornotemark[1]
\email{r@s.com}
\affiliation{\institution{Institute}}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

@@

Our corpus is assembled from three sources: the \emph{Base} libraries that are
bundled with the language implementation, packages hosted on \emph{CRAN} and
scripts from \emph{Kaggle}.

\mypara{Base.} The base dataset contains 13 core libraries performing basic
arithmetics, statistics, and operating system related functionalities. These
libraries are bundled with R and are executed pervasively.

\mypara{CRAN.} The Comprehensive R Archive
Network\footnote{\url{cran.r-project.org}} is the largest curated repository of
R packages. It hosts \CranAvailablePackagesRnd packages with 6 new one submitted
each day~\cite{Ligges2017}. Packages accepted to CRAN are authored by
experienced developers and abide to a number of well-formedness rules
automatically checked on each commit. Furthermore, each package comes with
sample data. There are three sources of runnable code in a package: \emph{tests,
examples} and \emph{vignettes} -- respectively, unit tests, code snippets from
the documentation, and long-form use-cases written in RMarkdown.
Examples and vignettes can be turned into scripts by extracting the relevant
code. We obtained \CranPackages that call \eval. These packages represent
\CranPackagesRatio of all packages or \CranCodeRatio of the entire code size of
CRAN. From these we extracted \CranRunnableScripts scripts that contain
\CranRunnableCode lines of code (\CranRunnableCodeExamplesRnd in examples,
\CranRunnableCodeVignettesRnd in vignettes and \CranRunnableCodeTestsRnd in
tests).

@@

The analysis presented in this has been automated by a pipeline that acquires
packages, extract scripts, executes them, traces their behavior and summarizes
observations. Figure~\ref{fig:pipeline} shows the main steps along with their
running time, data size, and number of elements manipulated. Timings are from a
cluster of three 2.3GHz Intel Xeon 6140 servers, with 72 cores and 256GB of RAM,
and shared OCFS network storage. The pipeline steps are:

@@

\medskip
\begin{compactenum}
\item \emph{Download.} Packages are downloaded from CRAN. For scripts, a web
  crawler retrieves code and the Kaggle command line tool gets data.
  Installation is complicated by native dependencies which are not properly
  documented and thus hard to automatically resolve.
\item \emph{Extract.} Given installed packages and scripts, the next step is to
  create runnable programs. The \genthat tool helpfully extracts all runnable
  code snippets from a package and turns each of these into a self-standing
  program~\cite{issta18}. Some Kaggle kernels are already scripts, for those
  nothing more needs be done. Others kernels are packages as notebooks, either
  as Rmarkdown or Jupyter, for those we use \c{knitr} to extract runnable code.
  The body of each extracted program is instrumented with calls our dynamic
  analyzer to ensure that we only record calls to \eval from the code of
  interest and not from bootstrapping or execution harness operations.
\item \emph{Trace.} Each program is executed using our dynamic analysis tool
  which is heavily instrumented interpreter that captures calls to \eval and
  many other fine-grained runtime events. Packages are run twice, once to
  capture \eval calls originating from package code, and a second time to
  capture calls coming from the base libraries. To avoid any interference, each
  program is run in its own process.
\item \emph{Analyze.} Finally, analysis output is merged, cleaned and summarized
  in a post-processing phase driven by series of R scripts. The summarized data
  is then analyzed in RMarkdown notebooks to gather insights. All figures and
  numbers appearing in the paper are generated automatically. Figures are
  produced in PDF by \c{ggplot2}, numbers are exported as \LaTeX macros.
\end{compactenum}

@@

\begin{wrapfigure}{r}{5.8cm}
 \includegraphics[width=0.5\textwidth, trim=4.8cm 0 6cm 0, clip]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

@@
